\section{Data Aquisition}
\subsection{Dataset}
Dive depth profile of Weddell seal DRE2015\_wed\_a\_m\_04 from Drescher Inlet.
\url{https://doi.pangaea.de/10.1594/PANGAEA.874281}

\subsection{Questions}
\subsubsection*{Who created the dataset (e.g., which team, research group) and on behalf of which entity (e.g., company, institution, organization)?(3.1)?}
The dataset was created by a researcher group of the Alfred Wegener Institute, Helmholtz Centre for Polar and Marine Research in Bremerhaven for the Marine Mammal Tracking Project
\subsubsection*{What data does each instance consist of (3.2)?}
The DTDP data was processed to eliminate visible short deviation during exposure every time a picture was taken.
Also dives with a pressure transducer offset greater than 20 m were removed.
\subsubsection*{How was the data associated with each instance acquired (3.3)?}
The data was aquired by sensors that were attached on the seals.
\subsubsection*{Was any preprocessing/cleaning/labeling of the data done (3.4)?}
Yes, there was data cleaning like already described in the question of 3.2.
\subsubsection*{Has the dataset been used for any tasks already (3.5)?}
The data was used in combination with images that were also taken by the seals to analyze under ice shelf enviroment.
\subsubsection*{Will the dataset be distributed to third parties outside of the entity on behalf of which the dataset was created (3.6)?}
The dataset is publicly available on \url{https://pangaea.de}
\subsubsection*{How can the owner/curator/manager of the dataset be contacted (3.7)?}
The owner can be contacted via email.

\subsection{Relevance}
The question "Has the dataset been used for any tasks already?" is particularly relevant for understanding the practical applications and scientific contributions of the dataset.
Knowing how the data has been utilized in previous tasks can provide insights into its potential uses for other fields like the impact of climate change.